---
title: "NYC_Property_Sales Data"
author: "@Vishwareeta"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    smooth_scroll: true
---

```{r setup, include=FALSE}
source("Import.R")
source("CodeFor2014.R")
source("CodeFor2015.R")
source("CodeFor2016.R")
source("CodeFor2017.R")
source("CodeFor2018.R")
source("CodeFor14To18.R")
```

2014
=======================================================================
Row
-----------------------------------------------------------------------

### Yearly Sales

```{r fig.height = 5, fig.width = 10}
Monthly2014 %>%
  hchart("line", hcaes(x = Month, y = Total_Sales),color="red")
```

Row {.tabset}
-----------------------------------------------------------------------

### JAN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==1,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### FEB

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==2,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==3,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### APR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==4,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAY

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==5,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==6,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUL

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==7,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### AUG

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==8,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### SEP

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==9,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### OCT

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==10,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### NOV

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==11,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### DEC

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2014[sales_by_week2014$month==12,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```


2014
=======================================================================
Row
-----------------------------------------------------------------------

### TRANSFER OF PROPERTY OWNERSHIP WITHOUT CASH CONSIDERATION

```{r}
articles <- Nul2014
valueBox(articles, icon = "fa-pencil")
```

### TOTAL DATA OBSERVATIONS

```{r}
articles <- Total2014
valueBox(articles, icon = "fa-pencil")
```

Row 
-----------------------------------------------------------------------

### BOROUGH

```{r}
Borough2014 %>%
  hchart("pie", hcaes(x = Borough, y = Total_Sales))
```

### TAX CLASS AT THE PRESENT

```{r}
TaxPres2014 %>%
  hchart("column", hcaes(x = Tax_At_Present, y = Total_Sales),color = "blue", borderColor = "black")
```

### YEAR BUILT

```{r}
Year2014 %>%
  hchart("pie", hcaes(x = Year_Built, y = Total_Sales))
```

Row 
-----------------------------------------------------------------------

### EASEMENT

```{r}
Ease2014 %>%
  hchart(
    "column", hcaes(x = Easement, y = Total_Sales),color = "blue", borderColor = "black")
```

### ZIP CODE

```{r}
Zip2014 %>%
  hchart(
    "pie", hcaes(x = Zipcode, y = Total_Sales))
```

### THE TOP 10 NEIGHBORHOODS

```{r}
Nei2014 %>%
  hchart("column", hcaes(x = Neighborhood, y = Total_Sales),color = "violet", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 BUILDING CLASS EARLIER

```{r}
Bui2014 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "Pink", borderColor = "black")
```

### TAX CLASS AT SALES TIME

```{r}
Tax2014 %>%
  hchart("column", hcaes(x = Tax_Class_Category, y = Total_Sales),color = "orange", borderColor = "black")
```

### THE TOP 10 BUILDING CLASS AT SALES TIME

```{r}
BuiSales2014 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "pink", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 RESIDENTAL UNITS

```{r}
Res2014 %>%
  hchart("column", hcaes(x = Residental_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

### THE TOP 10 COMMERCIAL UNITS

```{r}
Com2014 %>%
  hchart("column", hcaes(x = Commercial_units, y = Total_Sales),color = "violet", borderColor = "black")
```

### THE TOP 10 TOTAL UNITS

```{r}
Tot2014 %>%
  hchart("column", hcaes(x = Total_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 LAND SQUARE FEET

```{r}
Lan2014 %>%
  hchart("column", hcaes(x = Land_Square_Feet, y = Total_Sales),color = "pink", borderColor = "black")
```

### THE TOP 10 GROSS SQUARE FEET

```{r}
Gro2014 %>%
  hchart("column", hcaes(x = Gross_Square_Feet, y = Total_Sales),color = "orange", borderColor = "black")
```


2015
=======================================================================
Row
-----------------------------------------------------------------------

### Yearly Sales

```{r fig.height = 5, fig.width = 10}
Monthly2015 %>%
  hchart("line", hcaes(x = Month, y = Total_Sales),color="red")
```

Row {.tabset}
-----------------------------------------------------------------------

### JAN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==1,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### FEB

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==2,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==3,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### APR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==4,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAY

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==5,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==6,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUL

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==7,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### AUG

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==8,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### SEP

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==9,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### OCT

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==10,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### NOV

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==11,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### DEC

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2015[sales_by_week2015$month==12,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```


2015
=======================================================================
Row
-----------------------------------------------------------------------

### TRANSFER OF PROPERTY OWNERSHIP WITHOUT CASH CONSIDERATION

```{r}
articles <- Nul2015
valueBox(articles, icon = "fa-pencil")
```

### TOTAL DATA OBSERVATIONS

```{r}
articles <- Total2015
valueBox(articles, icon = "fa-pencil")
```

Row 
-----------------------------------------------------------------------

### BOROUGH

```{r}
Borough2015 %>%
  hchart("pie", hcaes(x = Borough, y = Total_Sales))
```

### TAX CLASS AT THE PRESENT

```{r}
TaxPres2015 %>%
  hchart("column", hcaes(x = Tax_At_Present, y = Total_Sales),color = "blue", borderColor = "black")
```

### YEAR BUILT

```{r}
Year2015 %>%
  hchart("pie", hcaes(x = Year_Built, y = Total_Sales))
```

Row 
-----------------------------------------------------------------------

### EASEMENT

```{r}
Ease2015 %>%
  hchart(
    "column", hcaes(x = Easement, y = Total_Sales),color = "blue", borderColor = "black")
```

### ZIP CODE

```{r}
Zip2015 %>%
  hchart(
    "pie", hcaes(x = Zipcode, y = Total_Sales))
```

### THE TOP 10 NEIGHBORHOODS

```{r}
Nei2015 %>%
  hchart("column", hcaes(x = Neighborhood, y = Total_Sales),color = "violet", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 BUILDING CLASS EARLIER

```{r}
Bui2015 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "Pink", borderColor = "black")
```

### TAX CLASS AT SALES TIME

```{r}
Tax2015 %>%
  hchart("column", hcaes(x = Tax_Class_Category, y = Total_Sales),color = "orange", borderColor = "black")
```

### THE TOP 10 BUILDING CLASS AT SALES TIME

```{r}
BuiSales2015 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "pink", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 RESIDENTAL UNITS

```{r}
Res2015 %>%
  hchart("column", hcaes(x = Residental_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

### THE TOP 10 COMMERCIAL UNITS

```{r}
Com2015 %>%
  hchart("column", hcaes(x = Commercial_units, y = Total_Sales),color = "violet", borderColor = "black")
```

### THE TOP 10 TOTAL UNITS

```{r}
Tot2015 %>%
  hchart("column", hcaes(x = Total_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 LAND SQUARE FEET

```{r}
Lan2015 %>%
  hchart("column", hcaes(x = Land_Square_Feet, y = Total_Sales),color = "pink", borderColor = "black")
```

### THE TOP 10 GROSS SQUARE FEET

```{r}
Gro2015 %>%
  hchart("column", hcaes(x = Gross_Square_Feet, y = Total_Sales),color = "orange", borderColor = "black")
```


2016
=======================================================================
Row
-----------------------------------------------------------------------

### Yearly Sales

```{r fig.height = 5, fig.width = 10}
Monthly2016 %>%
  hchart("line", hcaes(x = Month, y = Total_Sales),color="red")
```

Row {.tabset}
-----------------------------------------------------------------------

### JAN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==1,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### FEB

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==2,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==3,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### APR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==4,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAY

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==5,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==6,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUL

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==7,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### AUG

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==8,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### SEP

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==9,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### OCT

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==10,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### NOV

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==11,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### DEC

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2016[sales_by_week2016$month==12,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```


2016
=======================================================================
Row
-----------------------------------------------------------------------

### TRANSFER OF PROPERTY OWNERSHIP WITHOUT CASH CONSIDERATION

```{r}
articles <- Nul2016
valueBox(articles, icon = "fa-pencil")
```

### TOTAL DATA OBSERVATIONS

```{r}
articles <- Total2016
valueBox(articles, icon = "fa-pencil")
```

Row 
-----------------------------------------------------------------------

### BOROUGH

```{r}
Borough2016 %>%
  hchart("pie", hcaes(x = Borough, y = Total_Sales))
```

### TAX CLASS AT THE PRESENT

```{r}
TaxPres2016 %>%
  hchart("column", hcaes(x = Tax_At_Present, y = Total_Sales),color = "blue", borderColor = "black")
```

### YEAR BUILT

```{r}
Year2016 %>%
  hchart("pie", hcaes(x = Year_Built, y = Total_Sales))
```

Row 
-----------------------------------------------------------------------

### EASEMENT

```{r}
Ease2016 %>%
  hchart(
    "column", hcaes(x = Easement, y = Total_Sales),color = "blue", borderColor = "black")
```

### ZIP CODE

```{r}
Zip2016 %>%
  hchart(
    "pie", hcaes(x = Zipcode, y = Total_Sales))
```

### THE TOP 10 NEIGHBORHOODS

```{r}
Nei2016 %>%
  hchart("column", hcaes(x = Neighborhood, y = Total_Sales),color = "violet", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 BUILDING CLASS EARLIER

```{r}
Bui2016 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "Pink", borderColor = "black")
```

### TAX CLASS AT SALES TIME

```{r}
Tax2016 %>%
  hchart("column", hcaes(x = Tax_Class_Category, y = Total_Sales),color = "orange", borderColor = "black")
```

### THE TOP 10 BUILDING CLASS AT SALES TIME

```{r}
BuiSales2016 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "pink", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 RESIDENTAL UNITS

```{r}
Res2016 %>%
  hchart("column", hcaes(x = Residental_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

### THE TOP 10 COMMERCIAL UNITS

```{r}
Com2016 %>%
  hchart("column", hcaes(x = Commercial_units, y = Total_Sales),color = "violet", borderColor = "black")
```

### THE TOP 10 TOTAL UNITS

```{r}
Tot2016 %>%
  hchart("column", hcaes(x = Total_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 LAND SQUARE FEET

```{r}
Lan2016 %>%
  hchart("column", hcaes(x = Land_Square_Feet, y = Total_Sales),color = "pink", borderColor = "black")
```

### THE TOP 10 GROSS SQUARE FEET

```{r}
Gro2016 %>%
  hchart("column", hcaes(x = Gross_Square_Feet, y = Total_Sales),color = "orange", borderColor = "black")
```



2017
=======================================================================
Row
-----------------------------------------------------------------------

### Yearly Sales

```{r fig.height = 5, fig.width = 10}
Monthly2017 %>%
  hchart("line", hcaes(x = Month, y = Total_Sales),color="red")
```

Row {.tabset}
-----------------------------------------------------------------------

### JAN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==1,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### FEB

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==2,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==3,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### APR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==4,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAY

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==5,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==6,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUL

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==7,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### AUG

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==8,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### SEP

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==9,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### OCT

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==10,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### NOV

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==11,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### DEC

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2017[sales_by_week2017$month==12,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```


2017
=======================================================================
Row
-----------------------------------------------------------------------

### TRANSFER OF PROPERTY OWNERSHIP WITHOUT CASH CONSIDERATION

```{r}
articles <- Nul2017
valueBox(articles, icon = "fa-pencil")
```

### TOTAL DATA OBSERVATIONS

```{r}
articles <- Total2017
valueBox(articles, icon = "fa-pencil")
```

Row 
-----------------------------------------------------------------------

### BOROUGH

```{r}
Borough2017 %>%
  hchart("pie", hcaes(x = Borough, y = Total_Sales))
```

### TAX CLASS AT THE PRESENT

```{r}
TaxPres2017 %>%
  hchart("column", hcaes(x = Tax_At_Present, y = Total_Sales),color = "blue", borderColor = "black")
```

### YEAR BUILT

```{r}
Year2017 %>%
  hchart("pie", hcaes(x = Year_Built, y = Total_Sales))
```

Row 
-----------------------------------------------------------------------

### EASEMENT

```{r}
Ease2017 %>%
  hchart(
    "column", hcaes(x = Easement, y = Total_Sales),color = "blue", borderColor = "black")
```

### ZIP CODE

```{r}
Zip2017 %>%
  hchart(
    "pie", hcaes(x = Zipcode, y = Total_Sales))
```

### THE TOP 10 NEIGHBORHOODS

```{r}
Nei2017 %>%
  hchart("column", hcaes(x = Neighborhood, y = Total_Sales),color = "violet", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 BUILDING CLASS EARLIER

```{r}
Bui2017 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "Pink", borderColor = "black")
```

### TAX CLASS AT SALES TIME

```{r}
Tax2017 %>%
  hchart("column", hcaes(x = Tax_Class_Category, y = Total_Sales),color = "orange", borderColor = "black")
```

### THE TOP 10 BUILDING CLASS AT SALES TIME

```{r}
BuiSales2017 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "pink", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 RESIDENTAL UNITS

```{r}
Res2017 %>%
  hchart("column", hcaes(x = Residental_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

### THE TOP 10 COMMERCIAL UNITS

```{r}
Com2017 %>%
  hchart("column", hcaes(x = Commercial_units, y = Total_Sales),color = "violet", borderColor = "black")
```

### THE TOP 10 TOTAL UNITS

```{r}
Tot2017 %>%
  hchart("column", hcaes(x = Total_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 LAND SQUARE FEET

```{r}
Lan2017 %>%
  hchart("column", hcaes(x = Land_Square_Feet, y = Total_Sales),color = "pink", borderColor = "black")
```

### THE TOP 10 GROSS SQUARE FEET

```{r}
Gro2017 %>%
  hchart("column", hcaes(x = Gross_Square_Feet, y = Total_Sales),color = "orange", borderColor = "black")
```



2018
=======================================================================
Row
-----------------------------------------------------------------------

### Yearly Sales

```{r fig.height = 5, fig.width = 10}
Monthly2018 %>%
  hchart("line", hcaes(x = Month, y = Total_Sales),color="red")
```

Row {.tabset}
-----------------------------------------------------------------------

### JAN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==1,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### FEB

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==2,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==3,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### APR

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==4,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### MAY

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==5,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUN

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==6,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### JUL

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==7,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### AUG

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==8,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### SEP

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==9,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### OCT

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==10,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### NOV

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==11,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```

### DEC

```{r fig.height = 5, fig.width = 10}
ggplot((sales_by_week2018[sales_by_week2018$month==12,]),aes(x=week, y=Total_Sales)) +
  geom_bar(stat="identity", color="blue", fill="white")+
  theme(axis.text.x=element_text(angle=90,hjust=0.3))+
  coord_flip()+
  geom_text(aes(label=Total_Sales))
```


2018
=======================================================================
Row
-----------------------------------------------------------------------

### TRANSFER OF PROPERTY OWNERSHIP WITHOUT CASH CONSIDERATION

```{r}
articles <- Nul2018
valueBox(articles, icon = "fa-pencil")
```

### TOTAL DATA OBSERVATIONS

```{r}
articles <- Total2018
valueBox(articles, icon = "fa-pencil")
```

Row 
-----------------------------------------------------------------------

### BOROUGH

```{r}
Borough2018 %>%
  hchart("pie", hcaes(x = Borough, y = Total_Sales))
```

### TAX CLASS AT THE PRESENT

```{r}
TaxPres2018 %>%
  hchart("column", hcaes(x = Tax_At_Present, y = Total_Sales),color = "blue", borderColor = "black")
```

### YEAR BUILT

```{r}
Year2018 %>%
  hchart("pie", hcaes(x = Year_Built, y = Total_Sales))
```

Row 
-----------------------------------------------------------------------

### EASEMENT

```{r}
Ease2018 %>%
  hchart(
    "column", hcaes(x = Easement, y = Total_Sales),color = "blue", borderColor = "black")
```

### ZIP CODE

```{r}
Zip2018 %>%
  hchart(
    "pie", hcaes(x = Zipcode, y = Total_Sales))
```

### THE TOP 10 NEIGHBORHOODS

```{r}
Nei2018 %>%
  hchart("column", hcaes(x = Neighborhood, y = Total_Sales),color = "violet", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 BUILDING CLASS EARLIER

```{r}
Bui2018 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "Pink", borderColor = "black")
```

### TAX CLASS AT SALES TIME

```{r}
Tax2018 %>%
  hchart("column", hcaes(x = Tax_Class_Category, y = Total_Sales),color = "orange", borderColor = "black")
```

### THE TOP 10 BUILDING CLASS AT SALES TIME

```{r}
BuiSales2018 %>%
  hchart("column", hcaes(x = Building_Class_Category, y = Total_Sales),color = "pink", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 RESIDENTAL UNITS

```{r}
Res2018 %>%
  hchart("column", hcaes(x = Residental_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

### THE TOP 10 COMMERCIAL UNITS

```{r}
Com2018 %>%
  hchart("column", hcaes(x = Commercial_units, y = Total_Sales),color = "violet", borderColor = "black")
```

### THE TOP 10 TOTAL UNITS

```{r}
Tot2018 %>%
  hchart("column", hcaes(x = Total_units, y = Total_Sales),color = "yellow", borderColor = "black")
```

Row 
-----------------------------------------------------------------------

### THE TOP 10 LAND SQUARE FEET

```{r}
Lan2018 %>%
  hchart("column", hcaes(x = Land_Square_Feet, y = Total_Sales),color = "pink", borderColor = "black")
```

### THE TOP 10 GROSS SQUARE FEET

```{r}
Gro2018 %>%
  hchart("column", hcaes(x = Gross_Square_Feet, y = Total_Sales),color = "orange", borderColor = "black")
```



2014-2018
=======================================================================
Row
-----------------------------------------------------------------------

### TOTAL SALES BY YEAR

```{r fig.height = 5, fig.width = 10}
Monthly %>% select(Sales2014,Sales2015,Sales2016,Sales2017,Sales2018,Month) %>% 
  gather("key", "value", Sales2014,Sales2015,Sales2016,Sales2017,Sales2018) %>%
  hchart(type='line', hcaes(x='Month', y='value', group='key'))
```

Row
-----------------------------------------------------------------------

### TOTAL SALES FROM 2014 TO 2018

```{r fig.height = 5, fig.width = 10}
Yearly %>%
  hchart("line", hcaes(x = YearMonth, y = Total_Sales),color="red")
```
